Rates of true polar wander in convecting planets

### 2014-02-05 tpw_rate.tex
Add keywords
Update .gitignore

% gjilguid2e.tex
% V2.0 released 1998 December 18
% V2.1 released 2003 October 7 -- Gregor Hutton, updated the web address for the style files.

\documentclass{gji}
\usepackage{timet}

\title[TPW Rates]
  {Rates of true polar wander in convecting planets}
\author[I. Rose and B. Buffett]
  {Ian Rose$^1$ and Bruce Buffett$^1$ \\
  $^1$ Department of Earth \& Planetary Science, University of California, Berkeley, CA 94720, USA.  E-mail: ian.rose@berkeley.edu
  }
\date{}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\volume{}
\pubyear{}

@@

\begin{keywords}
True polar wander; Earth's rotational stability; mantle convection; scaling analyses;
\end{keywords}

@@

@@

%\begin{thebibliography}{}
%\end{thebibliography}

%\bsp % ``This paper has been produced using the Blackwell
     %   Publishing GJI \LaTeXe\ class file.''

>>>>

% gjilguid2e.tex

%\documentclass[onecolumn]{gji}
\documentclass{gji}
\usepackage{timet}
\usepackage{amsmath}

\title[TPW Rates]
  {Rates of true polar wander in convecting planets}
\author[I. Rose and B. Buffett]
  {Ian Rose$^1$ and Bruce A. Buffett$^1$ \\
  $^1$ Department of Earth \& Planetary Science, University of California, Berkeley, CA 94720, USA.  E-mail: ian.rose@berkeley.edu
  }
\date{}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\volume{}
\pubyear{}

@@

\begin{keywords}
Earth rotation variations; Mantle processes; Dynamics: convection currents and mantle plumes; Planetary interiors; Numerical solutions; Paleomagnetism applied to tectonics.
\end{keywords}

@@

\section{Governing equations}

As mantle convection and rotational dynamics of planetary bodies are usually considered separately, some extra care must be taken to establish self-consistent governing equations.  
Here we consider a planet in a rotating reference frame with no internal heating in the incompressible Boussinesq approximation.  The equations for mass, momentum, and energy then read

\begin{equation}
\nabla \cdot {\bf v} = 0
\label{conserve_mass}
\end{equation}

\begin{equation}
\begin{aligned}
 \rho \left[ \frac{D \bf v}{D t} + \frac{d \bf \Omega}{dt} \times {\bf r} +  2 {\bf \Omega} \times {\bf v} + {\bf \Omega \times \Omega \times r} \right] \\ = - \nabla P + \nabla \cdot \left( \eta \nabla_s {\bf v} \right) + \rho {\bf g}
\label{navier_stokes}
\end{aligned}
\end{equation}

\begin{equation}
\frac{\partial T}{\partial t} + {\bf v} \cdot \nabla T = \kappa \nabla^2 T
\label{energy}
\end{equation}

along with the equation of state

\begin{equation}
\rho = \rho_0 \left( 1 - \alpha T \right)
\label{eos}
\end{equation}

Dimensional analysis of this system (c.f. \cite{barenblatt1996scaling}) requires seven nondimensional numbers to characterize it.

\section{Scaling}

\section{Rates of true polar wander}

\section{Numerical results}

\section{Discussion}

@@

\bibliographystyle{gji}
\bibliography{tpw_rate.bib}
